An Algebraic Theory File Synchronization

### 2015-12-25 2015/axioms.tex
Highlighting results that the listed rules are sufficient for an implementation

\begin{mydef}[$A\indep B$: Independent commands, sequences and sets]
Two commands $\cxynv$ and $\czwmv$ 
are independent, and we write $\cxynv\indep\czwmv$ if 
they have the same effect in either order and do not break all filesystems:
\[ \cxynv\cc\czwmv \equiv \czwnv\cc\cxynv \nequiv \cbrk. \]
For two sequences or unordered sets of commands $A$ and $B$ we write $A\indep B$ if
for all $\alpha$ in $A$ and all $\beta$ in $B$, $\alpha\indep\beta$.
\end{mydef}

>>>>

\begin{mydef}[$A\indep B$: Independent commands, sequences and sets]\label{def_indep}
Two commands $\cxynv$ and $\czwmv$ 
are independent, and we write $\cxynv\indep\czwmv$ if 
they have the same effect in either order and do not break all filesystems:
\[ \cxynv\cc\czwmv \equiv \czwnv\cc\cxynv \nequiv \cbrk. \]
For two sequences or unordered sets of commands $A$ and $B$ we write $A\indep B$ if
for all $\alpha$ in $A$ and all $\beta$ in $B$, $\alpha\indep\beta$.
\end{mydef}

### 2015-12-25 2015/rec-intro.tex
Highlighting results that the listed rules are sufficient for an implementation

\begin{mydef}[Reconciliation]\label{def:reconciliation}
We determine $\reca$---which we apply to $\FS_B$ 
to reconcile it with $\FS_A$---to be
the largest subset of $A\setminus B$
that is independent of $B\setminus A$:
\begin{align*}
\reca = \{\alpha|{}& \\
& \alpha\in A\setminus B \\
& \wedge \\
& \forall \beta\in B\setminus A: \alpha\indep\beta\\
\}. &
\end{align*}
The order of commands in the sequence can be determined using the algorithm described in
\cref{ordering} as any subset of $A$ is also simple.
In a similar way, $\recb$ can be obtained by reversing $A$ and $B$
in the definition.
\end{mydef}

We would now like to prove that $\reca$ and $\recb$ can be applied to the replicas,
that is, without loss of generality,
\[ \reca\aFS_B\neq\fsbroken. \]
So that we can formalize statements needed to prove this,
let us introduce two relations that describe under what conditions
sequences of commands work, that is, do not break a filesystem.

>>>>

\begin{mydef}[Reconciliation]\label{def:reconciliation}
We determine $\reca$---which we apply to $\FS_B$ 
to reconcile it with $\FS_A$---to be
the largest subset of $A\setminus B$
that is independent of $B\setminus A$:
\begin{align*}
\reca = \{\alpha|{}& \\
& \alpha\in A\setminus B \\
& \wedge \\
& \forall \beta\in B\setminus A: \alpha\indep\beta\\
\}. &
\end{align*}
\end{mydef}

Whether two commands are independent is easy to determine programmatically
either based on \cref{def_indep} and the rules listed in \cref{section_axioms},
or based on \cref{incomparable_is_independent} 
in at most $O(x^2)$ time, where $x$ is the number of commands.
Then, to generate the sequence $\reca$ from the resulting set, 
we order the commands using the algorithm described in
\cref{ordering} as any subset of $A$ is also simple.

$\recb$ can be obtained in a similar way by reversing $A$ and $B$
in the definition.

\bigskip

\noindent
Next, we would now like to prove that $\reca$ and $\recb$ can be applied to the replicas,
that is, without loss of generality,
\[ \reca\aFS_B\neq\fsbroken. \]
So that we can formalize statements needed to prove this,
let us introduce two relations that describe under what conditions
sequences of commands work, that is, do not break a filesystem.

### 2015-12-25 2015/works-inverse.tex
Highlighting results that the listed rules are sufficient for an implementation

\begin{mydef}[$\works{x}$]
% Unsure if this relation should be in the algebra.
For a set of $k$ sequences
$\works{A_1,A_2,\ldots,A_k}$ means that 
$A_1,A_2,\ldots,A_k$ work at the same time, that is,
% intended interpretation:
\[\exists \FS: A_1\FS\neq\fsbroken \wedge \cdots \wedge A_k\FS\neq\fsbroken\]
As the sequences form a set, their order is irrelevant.
% inference rules:
We also know that $\works{A} \Leftrightarrow A\nequiv \cbrk$. 
\end{mydef}

@@

\begin{mydef}[Sets of sequences]
For brevity, we will use calligraphic letters (e.g. $\seqset{A, B, C}$ and $\seqset{S}$)
to denote sets of sequences,
and, in general, $A\cc\seqset{B}$ to note the set of sequences $\{A\cc B|B\in\seqset{B}\}$.
\end{mydef}

>>>>

\begin{mydef}[$\works{x}$]
% Unsure if this relation should be in the algebra.
For a set of $k$ sequences
$\works{A_1,A_2,\ldots,A_k}$ means that 
$A_1,A_2,\ldots,A_k$ work at the same time, that is,
% intended interpretation:
\[\exists \FS: A_1\FS\neq\fsbroken \wedge \cdots \wedge A_k\FS\neq\fsbroken.\]
As the sequences form a set, their order is irrelevant.
% inference rules:
We also know that $\works{A} \Leftrightarrow A\nequiv \cbrk$. 
\end{mydef}

@@

\begin{mydef}[Sets of sequences]
For brevity, we will use calligraphic letters (e.g. $\seqset{A, B, C}$ and $\seqset{S}$)
to denote sets of sequences,
and use $A\cc\seqset{B}$ to denote the set of sequences $\{A\cc B|B\in\seqset{B}\}$.
\end{mydef}
